JWST Noise Floor I: Systematic Error Sources in JWST NIRCam Time Series

### 2020-05-12 ms.tex
following request to move from possible author to aknowledgements
fixed tiny inconsistency in the faint source example

\author{Peiman Maghami?}

@@

We note that Figure \ref{fig:genericSourceErrorContrib} shows a somewhat counter-intuitive result: read noise dominates for bright source and becomes less important for faint sources.
For typical observations, such as faint galaxies or distant stars, the opposite is true: read noise is more of a concern for faint sources than bright ones.
So why is there a discrepancy?
The difference in these two science cases is that for exoplanet transit observations, the detector well depth is filled to approximately the same level ($\sim 32,000$ DN or 50\% well depth per pixel) regardless if the system's magnitude is 6 or 11.
For the bright source with a few groups up the ramp, the read noise will be a larger fraction of 32,000 DN than for a faint source with many groups up the ramp.
This is different from a faint galaxy in the $K > 22$ range, which will not fill the detector well.
For a fixed exposure time, a $K=25$ and $K=20$ galaxies would be observed with approximately the same number of groups per integration so the read noise in DN from each source in an integration would be approximately the same whereas the number of DN from the source per integration would be 100 times larger for the $K=20$ galaxy.

@@

\section*{acknowledgements}
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.

>>>>

@@

We note that Figure \ref{fig:genericSourceErrorContrib} shows a somewhat counter-intuitive result: read noise dominates for bright source and becomes less important for faint sources.
For typical observations, such as faint galaxies or distant stars, the opposite is true: read noise is more of a concern for faint sources than bright ones.
So why is there a discrepancy?
The difference in these two science cases is that for exoplanet transit observations, the detector well depth is filled to approximately the same level ($\sim 32,000$ DN or 50\% well depth per pixel) regardless if the system's magnitude is 6 or 11.
For the bright source with a few groups up the ramp, the read noise will be a larger fraction of 32,000 DN than for a faint source with many groups up the ramp.
This is different from a faint galaxy in the $K > 20$ range, which will not fill the detector well.
For a fixed exposure time, a $K=25$ and $K=20$ galaxies would be observed with approximately the same number of groups per integration so the read noise in DN from each source in an integration would be approximately the same whereas the number of DN from the source per integration would be 100 times larger for the $K=20$ galaxy.

@@

\section*{acknowledgements}
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
Thanks to Peiman Maghami for providing the line of site pointing jitter simulation for use in estimating the subpixel sensitivity as well explaining sources of pointing error.
